%-------------------------
% Resume in Latex
% Author : Cyrus
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{-4pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{\small #3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Cyrus Shekari} \\ \vspace{3pt}
    \small \faPhone* 000.000.0000 \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{1pt} \href{mailto:aaaaaaa@gmail.com}{\underline{aaaaaaa@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{1pt} \href{https://www.linkedin.com/in/aaaaa}{\underline{linkedin.com/aaaaa}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{1pt} \href{https://github.com/cyshek}{\underline{github.com/cyshek}}
\end{center}


%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{August 2021 -- December 2024}
      {Bachelor of Computer Science, Minor in Mathematics, GPA: 3.8}{Houston, TX}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Databases, Artificial Intelligence, Machine Learning, Data Science}
        \resumeItem 
            {\textbf{Honors}: Academic Excellence Scholarship, Dean’s List Distinguished Scholar, Phi Beta Kappa}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon Robotics}{August 2024 -- December 2024}
      {Product Manager Intern}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Led 8 sprint planning and retrospectives, resolving 40+ support tickets to reduce intake queues in collaboration with developers}
        \resumeItem{Automated the identification of 1,200+ legacy stations by developing a Python query to filter through 11,000+ JSON entries}
        \resumeItem{Piloted an OS migration initiative, coordinating with IT managers to successfully migrate three sites, each with 400+ stations}
        \resumeItem{Engaged with 5 customers to align on CI/CD integration strategies, deploying automated pipelines on AWS to streamline updates}
        \resumeItem{Designed Excel graphs and Smartsheet schedules to track sprint performance metrics and align deliverables for pipeline creation}
        \resumeItem{Authored wikis and handoff documentation for QA testing of new features, reducing customer support inquiries by 23\%}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{May 2024 -- August 2024}
      {Technical Program Manager Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Enhanced an \textbf{AI/ML chatbot integration} to automate Azure service team workflows, saving \textbf{37 hours} of developer time monthly.}
        \resumeItem{Facilitated demos with 14 Azure service teams, driving technology adoption and identifying additional feature requirements.}
        \resumeItem{Authored 2 feature releases, enabling user-created custom presets and migrating service team workflows to AWS Step Functions.}
        \resumeItem{Researched the feasibility of converting service team XAML workflows to YAML using AI/ML, identifying a potential \textbf{22\% increase} in buildout speed.} 
      \resumeItemListEnd
    
    \resumeSubheading
      {Microsoft}{May 2023 -- August 2023}
      {Technical Program Manager Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Developed a white paper illustrating a comprehensive approach to understanding, tracking, and reducing toil, resulting in a potential \textbf{28\% faster launch} and approximately \textbf{\$3 million in increased revenue} per region buildout.}
        \resumeItem{Analyzed incident counts and automation for 140+ Azure service teams through Kusto queries, orchestration platform workflows, and Power BI dashboards, revealing that 63\% of teams were not automated.}
        \resumeItem{Conducted interviews with 20+ Azure service teams, uncovering operational inefficiencies and identifying toil's contribution of 81 additional hours of manual work per geo-expansion buildout.}
        \resumeItem{Devised a \textbf{Power BI dashboard} integrating data from Excel, Azure Geo Expansion Portal, and Azure Data Explorer to \textbf{track toil across 140+ service teams}, enabling prioritization of support for teams experiencing high toil.}
      \resumeItemListEnd

    \resumeSubheading
      {Pro Painters}{May 2022 -- October 2022}
      {Project Manager Intern}{Houston, TX}
      \resumeItemListStart
        \resumeItem{Matched over \textbf{1000 material invoices} and employee payroll documents with the corresponding painting jobs, determining profit margins of each painting job with tools, such as QuickBooks and Microsoft Excel.}
        \resumeItem{Coordinated with project managers to send over 200 proposals and invoices, leading to \textbf{26\% more jobs} being booked monthly.}
        \resumeItem{Updated Pro Painters website with WordPress and Pro Painters Google business profile, boosting conversion rates by 2.71\%.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{PERSONAL PROJECTS}
    \resumeSubHeadingListStart 
    \resumeProjectHeading
        {\textbf{Chat App}}{September 2023 -- November 2023}
        \resumeItemListStart
            \resumeItem{Innovated with \textbf{React.js, Node.js, CSS, and Socket.io} enabling efficient bi-directional communication between front end and back end, allowing users in the same chat room to quickly send and receive texts in real-time.}
            \resumeItem{Created web server with Express.js and Node.js to permit push capabilities. Updated message display with React.js.}
        \resumeItemListEnd        

    \resumeProjectHeading
        {\textbf{Heart Failure Prediction}}{June 2022 -- July 2022}
        \resumeItemListStart
            \resumeItem{Implemented machine learning classification models, such as decision trees, neural networks, and logistic regression, using scikit-learn (sklearn) to predict patient mortality from heart failure, achieving an \textbf{accuracy of 81 - 85\%} per model.}
            %\resumeItem{Preprocessed and cleaned \textbf{1000+ observations} using one-hot encoding with pandas on the patient information data frame.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXTRACURRICULAR-----------
\section{EXTRACURRICULAR}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CougarStrength}{August 2021 -- Present}
      {President}{Houston, TX}
      \resumeItemListStart      
        \resumeItem{Organized strength training classes on campus for \textbf{20+ members 3 times a week} to improve student health and well-being.}
        \resumeItem{Lead the creation and distribution of 100+ flyers advertising the club, fostering a \textbf{30\% boost} in new members.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}: {C++, C\#, Python, R, Java, JavaScript, React.js, Node.js, HTML, CSS, SQL, KQL}\vspace{2pt} \\
     \textbf{Tools}:     {AWS, AI/ML, Microsoft Azure, Power BI, Notion, Figma, Google Analytics, Microsoft Excel, QuickBooks, GitHub}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
